%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj + some brand new features from Mary Feofanova
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Zhuldyz Namazbayeva} & Email : \href{mailto:zhuldyznamazbayeva@gmail.com}{zhuldyznamazbayeva@gmail.com}\\
  Github: \href{https://github.com/znamazbayeva}{znamazbayeva} & Mobile : +7\hspace{0.5ex}707\hspace{0.5ex}556\hspace{0.5ex}65\hspace{0.5ex}44 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {Nazarbayev University}{Nur-Sultan, Kazakhstan}
    {Bachelor of Computer Science}{August 2018 - May 2022}
	 %\begin{comment}
	 \resumeItemListStart
        \resumeItem{Relevant courses}
        {Algorithms, Data Structures, Microcontrollers, Computer Systems and Organization, Artificial Intelligence, Software Engineering, Discrete Mathematics, Calculus, Linear Algebra, Database Systems, Deep Learning}
      \resumeItemListEnd
      %\end{comment}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeExpSubheading
      {\href{https://www.chocotravel.com}{Aviata}}{Almaty, Kazakhstan}
      {Frontend Developer Intern, Chocotravel App Team}{February 2022 - May 2022}
      {\skill{Vue.js} \skill{Tailwind CSS} \skill{PHP} \skill{TypeScript}}
      \resumeDesc{
      \begin{itemize}
            \item Created new components and refactored the code from monolith to microservices architecture, which led to 2x server speed improvement of the avia and railways tickets reservation system used by more than \textbf{ 1 million people}.
          \item Fixed 20+ minor and major bugs, reducing the instances of bugs by 15\%.
      \end{itemize}}
      \resumeExpSubheading
      {\href{https://kazaerospace.kz}{KazAeroSpace}}{Nur-Sultan, Kazakhstan}
      {Frontend Developer Intern, 2DGIS Mapping Web Platform Team}{May 2021 - August 2021}
      { \skill{React.js}  \skill{Redux} \skill{TypeScript} \skill{OpenLayers} \skill{Python} \skill{Django} \skill{SQL}}
      \resumeDesc{
      \begin{itemize}
          \item Built functions for web mapping platform, which led to user-interface experience improvement.
          \item Improved the accuracy of the route-finding function by 10\% using Dijkstra’s algorithm.
      \end{itemize}}
      \resumeExpSubheading
      {Nazarbayev University}{Nur-Sultan, Kazakhstan}
      {Research Assistant}{January 2021 – June 2021}
      {\skill{Python} \skill{PyTorch} \skill{Research}}
      \resumeDesc{
      \begin{itemize}
          \item Assisted in developing Convolutional Neural Network classifiers for P300 signals in brain-computer interface system.
          \item Achieved the highest of 89\% accuracy by implementing one convolutional layer neural network and applying hyper-parameter tuning.
      \end{itemize}
      }
      \resumeExpSubheading
      {MethodPro}{Almaty, Kazakhstan}
      {SWE Intern}{June 2018 – August 2018}
      {\skill{Java} \skill{Python} \skill{SQL}}
      \resumeDesc{\begin{itemize}
          \item Developed a prototype of an Android mobile application with analytics, which is used by \textbf{80+ thousand customers }of company "Technodom", in team of 5 people.
      \end{itemize}}
       
    
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
  
      \resumeProjSubheading
      {\href{https://github.com/znamazbayeva/CSCI-361-term-project}{Web application of a hotel chain system}}{Nur-Sultan, Kazakhstan}
      {\skill{Java}\skill{JavaScript}\skill{MySQL} \skill{RestAPI}\skill{Maven}}{Autumn 2020}
          \resumeDesc{\begin{itemize}
           \item Developed a hotel room booking web app with Java server-side back-end, front-end and database in a team of 5 people.
           \item Took ownership of Middle Tier and Database Tier of the project and achieved delivery of all functionalities (sign-in, registration, bookings management and reservation creation) in an effective manner.
             \end{itemize}}
    % \resumeProjSubheading
    %   {\href{https://github.com/QratorLabs/inclickdb}{InclickDB}}{Moscow, Russia}
    %   {\skill{GoLang} \skill{Python} \skill{Grafana} \skill{Graphite} \skill{ClickHouse} \skill{InfluxDB}}{May 2019}
    %       \resumeDesc{Investigated possible solutions to a problem of migrating from InclickDB to ClickHouse for a monitoring system with tagged metrics. Created tag support in existing solution by teaching myself Golang and contributed to open-source: \href{https://github.com/lomik/carbon-clickhouse/pull/32}{pull-request}.}
          
    \begin{comment}  
    \resumeProjSubheading
      {\href{https://github.com/AndroidTopTeam/MyChief}{MyChief}}{Moscow, Russia}
      {\skill{Java} \skill{Android}}{Nov. 2017}
      \resumeDesc{Learned Android and implemented all structure and internal code logic (activities, fragments, lru cache) of mobile app that can search for recipes with ingredients entered by user, collaborated with a team of 3 students.}
    \end{comment}
      
  \resumeSubHeadingListEnd

\section{Achievements}
  \resumeSubHeadingListStart
    \item{
    \textbf{6th place out of 54 teams} at "AITUHACKDAY: Creative Industry" Hackathon in 2022 with analysis model.
  }
  \item{
    \textbf{1st place out of 18 teams} at MethodPro Hackathon in 2019 with Android rating application with analytics.
  }
    \item{
    \textbf{3rd place out of 40 teams} at Technovation Challenge in 2018 with IOS anonymous chat with psychologists app.
  }
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: JavaScript, Python, C++, Java }
   }\vspace{-7pt}
   \item{
     \textbf{Technologies}{: Vue.js, React.js, SQL, SpringBoot, Git, Node.js }
   }
   \vspace{-7pt}
   \item{
     \textbf{Knowledge}{: Algorithms, Data Structures, Concurrent Computing}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
